MSSM-Penn-Pitt - ACC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Model Selection

### 2020-05-04 individual-cohorts/MSSM-Penn-Pitt_ACC_FEATURECOUNTS_GRCh38_CQN.Rmd
fix parent id

```{r synapse.parameters, include=FALSE, cache=FALSE}
parentId = 'syn21435176';
activityName = 'Covariate adjustments';
activityDescription = 'Covariate analysis of GRCh38 feature counts with CQN normalisation (ACC)';

>>>>

```{r synapse.parameters, include=FALSE, cache=FALSE}
parentId = 'syn22012942';
activityName = 'Covariate adjustments';
activityDescription = 'Covariate analysis of GRCh38 feature counts with CQN normalisation (ACC)';
